¿Como disminuir la desigualdad del conocimiento civico?

### 2020-08-21 docs/prod_analysis.Rmd
sitio web
Se realiza un sitio para el articulo.

## ComparaciC3n de modelos 6-8
```{r results='asis'}
comp_model< list(results_6,results_7,results_8)
save(comp_model, file = "../output/graphs/comp_model.Rdata")
```

>>>>

## ComparaciC3n de modelos 6-8
```{r results='asis'}
save(results_6, file = "../output/graphs/results_6.Rdata")
save(results_7, file = "../output/graphs/results_7.Rdata")
save(results_8, file = "../output/graphs/results_8.Rdata")
